Neighbourhood

### 2023-02-27 docsrc/documentation/notebooks/household_income.Rmd

---
title: "Household Income"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # useful for debugging.
---

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r, hh_income_data}
continuous_density("hh_income")  
```

@@

```{r income_output, echo=FALSE}
options(width=120)
ols_output("../../../data/transitions/test/hh_income_2018_2019.rds")
ols_histogram("../../../data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
```

>>>>

---
title: "Household Income"
output: html_document
bibliography: 
  - "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # useful for debugging.
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```

```{r load_data, include=FALSE}
source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
```

@@

```{r, hh_income_data}
continuous_density("data/transitions/hh_income/ols/hh_income_2018_2019.rds", "next_hh_income")  
```

@@

```{r income_output, echo=FALSE}
options(width=120)
ols_output("data/transitions/hh_income/ols/hh_income_2018_2019.rds")
ols_histogram("data/transitions/hh_income/ols/hh_income_2018_2019.rds", "next_hh_income")
```

### 2023-02-27 docsrc/documentation/notebooks/neighbourhood.Rmd

---
title: "Neighbourhood"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

@@

```{r neighbourhood_setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r neighbourhood_barchart, echo=FALSE}
print(table(real_data$neighbourhood_safety))
discrete_barplot("neighbourhood_safety")
getwd()
```

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds", "neighbourhood_safety_next")
clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds")
```

>>>>

---
title: "Neighbourhood"
output: html_document
bibliography: 
  - "docsrc/refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

```{r load_data, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```

@@

```{r neighbourhood_setup, include=FALSE}
source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
```

@@

```{r neighbourhood_barchart, echo=FALSE}
discrete_barplot("data/transitions/neighbourhood_safety/clm/neighbourhood_safety_2014_2017.rds", 'next_neighbourhood_safety')
```

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("data/transitions/neighbourhood_safety/clm/neighbourhood_safety_2014_2017.rds", "next_neighbourhood_safety") 
clm_output("data/transitions/neighbourhood_safety/clm/neighbourhood_safety_2014_2017.rds")  
```
